Dotted Suffix Trees\\A Structure for Approximate Text Indexing

### 2005-08-30 paper/structure.tex
fix references
s/mississipi/mississippi/

\begin{figure}
\includegraphics{figures/mississipi-0}
\caption{Suffix Tree for the string \putstring{mississipi}}%
\label{fig:mississipi-0}
\end{figure}

Suffix Trees have become a well known structure since their introduction in 1973~\cite{weiner}. In Figure~\ref{fig:mississipi-0} we show the suffix tree for the string \putstring{mississipi}.

@@

In a suffix tree, it is possible to define a suffix link for each internal node. Both Ukkonen's~\cite{ukkonen} and McCreight's~\cite{mccreight} algorithms are linear time algorithms for constructing a suffix tree which includes suffix links. The suffix links are shown in Figure~\ref{fig:mississipi-0} as dotted links.

@@

For example, in the node $\overline{issi}$ in the suffix tree of Figure~\ref{fig:mississipi-0}, the occurrence set is $\{5, 2\}$ and its position set is $\{6, 9\}$. In a sense, one can say that being at node $\overline{issi}$ is being at positions 6 and~9 simultaneously. Note that for each node, the tree below it is the Patricia tree of the suffixes starting at the positions in its position set.

@@

For example, in the above mentioned node $\overline{issi}$, the error tree is formed by taking the strings starting at positions $\{7, 10\}$ (ie \putstring{sipi\$} and \putstring{i\$}) in a Patricia tree.

@@

\begin{figure} 
\includegraphics[width=\textwidth]{figures/mississipi-1.eps}
% mississipi-1.eps: 300dpi, width=6.08cm, height=1.63cm, bb=0 0 718 193
\caption{1-error dotted tree for \putstring{mississipi}}%
\label{fig:mississipi-1}
\end{figure}

The one-error dotted tree for \putstring{mississipi} is shown in Figure~\ref{fig:mississipi-1}. The nodes are connected to their error trees by diagonal links.

>>>>

\begin{figure}
\includegraphics{figures/mississippi-0}
\caption{Suffix Tree for the string \putstring{mississippi}}%
\label{fig:mississippi-0}
\end{figure}

Suffix Trees have become a well known structure since their introduction in 1973~\cite{weiner}. In Figure~\ref{fig:mississippi-0} we show the suffix tree for the string \putstring{mississippi}.

@@

In a suffix tree, it is possible to define a suffix link for each internal node. Both Ukkonen's~\cite{ukkonen} and McCreight's~\cite{mccreight} algorithms are linear time algorithms for constructing a suffix tree which includes suffix links. The suffix links are shown in Figure~\ref{fig:mississippi-0} as dotted links.

@@

For example, in the node $\overline{issi}$ in the suffix tree of Figure~\ref{fig:mississippi-0}, the occurrence set is $\{5, 2\}$ and its position set is $\{6, 9\}$. In a sense, one can say that being at node $\overline{issi}$ is being at positions 6 and~9 simultaneously. Note that for each node, the tree below it is the Patricia tree of the suffixes starting at the positions in its position set.

@@

For example, in the above mentioned node $\overline{issi}$, the error tree is formed by taking the strings starting at positions $\{7, 10\}$ (ie \putstring{sippi\$} and \putstring{i\$}) in a Patricia tree.

@@

\begin{figure} 
\includegraphics[width=\textwidth]{figures/mississippi-1.eps}
% mississippi-1.eps: 300dpi, width=6.08cm, height=1.63cm, bb=0 0 718 193
\caption{1-error dotted tree for \putstring{mississippi}}%
\label{fig:mississippi-1}
\end{figure}

The one-error dotted tree for \putstring{mississippi} is shown in Figure~\ref{fig:mississippi-1}. The nodes are connected to their error trees by thick diagonal links.
